Analysis : exp229 analysis

### 2018-12-08 resistingrhythm/analysis/exp229.Rmd
WIP

```{r, fig.width=1.4, fig.height=0.8}
# null_rate <- mean(filter(results229, osc_rate == "0")$rate_k)
results229 %>% 
  ggplot(aes(x=frac_tau_h, y=rate_k)) +
    geom_boxplot() +
    theme_classic2() +
    labs(x="Frac. tau_h", y="Pop. rate") +
    theme(legend.position = "right") 
```

@@

```{r, fig.width=1.2, fig.height=0.6}
results229 %>% 
  # filter(osc_rate == "4") %>%
  ggplot(aes(x=freq, y=rate_k, color=as.numeric(frac_tau_h), group=interaction(freq, frac_tau_h))) +
  geom_jitter(size=0.02, width=.2, alpha=0.5, outlier.colour = NA) +
  # geom_boxplot() +
  # geom_jitter() +
  theme_classic2() +
  scale_color_gradient(high="plum4", low="lightgrey") +
  labs(x="Frequency (Hz)", y="Pop. rate") +
  theme(legend.position = "none")
```

>>>>

```{r, fig.width=1.4, fig.height=0.8}
results229 %>% 
  filter(osc_rate == "6", freq =="8") %>% 
  ggplot(aes(x=frac_tau_h, y=rate_k)) +
    geom_jitter(size=0.01) +
    theme_classic2() +
    labs(x="Frac. tau_h", y="Pop. rate") +
    theme(legend.position = "right") 
```

```{r, fig.width=2, fig.height=1}
results229 %>% 
  filter(osc_rate == "6", freq =="8") %>% 
  group_by(osc_rate, frac_tau_h) %>%
  summarise(M=mean(rate_k), SD=sd(rate_k)) %>%
  ggplot(aes(x=frac_tau_h, y=M)) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.2, size=0.8)  +
  labs(y="Pop. rate", x="tau_h") +
  lims(y=c(0, 160))
```

```{r, fig.width=2.2, fig.height=1.2}
results229 %>% 
  filter(frac_tau_h == "2") %>% 
  filter(osc_rate != "0") %>% 
  ggplot(aes(x=osc_rate, y=rate_k)) +
    geom_boxplot() +
    theme_classic2() +
    labs(x="Osc rate", y="Pop. rate") +
    theme(legend.position = "right") 
```

@@

```{r, fig.width=1.2, fig.height=0.6}
results229 %>% 
  filter(osc_rate == "6") %>%
  ggplot(aes(x=freq, y=rate_k, color=as.numeric(frac_tau_h), group=interaction(freq, frac_tau_h))) +
  geom_jitter(size=0.02, width=.2, alpha=0.5, outlier.colour = NA) +
  # geom_boxplot() +
  # geom_jitter() +
  theme_classic2() +
  scale_color_gradient(high="plum4", low="lightgrey") +
  labs(x="Frequency (Hz)", y="Pop. rate") +
  theme(legend.position = "none")
```
